Free surface computations in mantle convection models

### 2015-11-06 free-surface-paper.tex
Fix typo
Add keywords
Fix up affiliations and acknowledgements

\usepackage{todonotes}
\newcommand\timo[1]{\todo[inline]{Timo: #1}}

@@

@@

\author{I. Rose, B. Buffett, and Timo Heister\fnref{ref3}}

\fntext[ref3]{\url{heister@clemson.edu}, partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award No. EAR-0949446 
and The University of California-Davis, and National Science Foundation grant DMS1522191.}

@@

Here we analyze the problem of creeping viscous flow with a free surface and discuss the 
origin of these instabilities. We demonstrate their cause and how existing stabilization 
schemes work to damp them out.
We also propose a new scheme for removing instabilites from free surface calculations. 
It does not require modifications to the system matrix, nor additional variables, but is instead
an explicit scheme based on nonstandard finite differences.  It relies on a single 
stabilization parameter which may be identified with the smallest relaxation timescale of the
free surface.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

@@

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\section{Bibliography}
\bibliographystyle{elsarticle-harv} 
\bibliography{free-surface-paper}

>>>>

@@

%% Block of code for fixing corresponding author bug 
%% in elsarticle template... Don't really understand it
\makeatletter
\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
    \def\baselinestretch{1}%
    \upshape\authorsep#1\unskip\textsuperscript{%
      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
      }%
    \def\authorsep{\unskip,\space}%
    \global\let\@fnmark\@empty
    \global\let\@corref\@empty  %% Added
    \global\let\sep\@empty}%
    \@eadauthor={#1}
}
\makeatother
%% End block of weird code

@@

\author{Ian Rose\corref{cor1}\fnref{ref1}}
\author{Bruce Buffett\fnref{ref1}}
\author{Timo Heister\fnref{ref2}}

\fntext[ref1]{University of California, Berkeley}
\fntext[ref2]{Clemson University}
\cortext[cor1]{Corresponding author, \url{ian.rose@berkeley.edu}}

@@

Here we analyze the problem of creeping viscous flow with a free surface and discuss the 
origin of these instabilities. We demonstrate their cause and how existing stabilization 
schemes work to damp them out.
We also propose a new scheme for removing instabilities from free surface calculations. 
It does not require modifications to the system matrix, nor additional variables, but is instead
an explicit scheme based on nonstandard finite differences.  It relies on a single 
stabilization parameter which may be identified with the smallest relaxation timescale of the
free surface.

@@

\begin{keyword}
Numerical modeling \sep
Free surface \sep
Mantle convection \sep
Geodynamics
%% keywords here, in the form: keyword \sep keyword

@@

\section*{Acknowledgements}
This work was supported through National Science Foundation grant EAR-1246670
and by the Computational Infrastructure in Geodynamics (CIG), through National Science Foundation grant EAR-0949446. 
TH is partially supported by NSF grant DMS-1522191.
Thanks to Wolfgang Bangerth and Brent Delbridge for useful discussions.
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

@@

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\section*{Bibliography}
\bibliographystyle{elsarticle-harv} 
\bibliography{free-surface-paper}
